WV -- interim report

### 2015-04-25 tussentijdsverslag/tussentijdsverslag.tex

\paragraph{Output of the Matlab script.} The results of the power
measurements done with the oscilloscope all return negative units of
work. We assume that this has to do either with flow of current inside
the measurement setup or with the Matlab scripte we use. We interpret
these measurements as unsigned units.

>>>>

% \paragraph{Output of the Matlab script.} The results of the power
% measurements done with the oscilloscope all return negative units of
% work. We assume that this has to do either with flow of current inside
% the measurement setup or with the Matlab scripte we use. We interpret
% these measurements as unsigned units.
